---
title: 'NFP: network fingerprint - a knowledge-based characterization of biomecial
  networks in R'
author: "Yang Cao, Haochen He"
output: html_document
data: xx.xx.xx
---

## Getting started

### Citation

To cite our *NFP* package:

```{R citation, eval = FALSE}
citation('NFP')
```
### Introduction

This manual is a brief introduction to structure, functions and usage of
*NFP* package. The *NFP* package provides a set of functions to
support knowledge-based network fingerprint (NFP) framework ,which was described by 
**reference1**. A biomedical network is characterized as a spectrum-like
vector called “network fingerprint”, which contains similarities to basic
reference networks. This framework provides a more intuitive way to decipher
molecular networks, especially for large-scale network comparisons and 
clustering analyses. (NFP方法和packag的简介，可以用来做什么：比如崔文章中的算例
通过映射不同疾病分子网络至参考网络可以发现疾病的关联，基于NFP对多种疾病分类等）

The three main features of *NFP*:

- Basic reference networks (KEGG signal pathway networks) generation.

- Network comparison, which encompasses network merging, annotation and 
similarity scoring,vstandardization.

- Network fingerprint visualization.

### Installation

*NFP* requires these packages: *magrittr*, *igraph*, *plyr*, *ggplot2*, *apcluster*, 
*dplyr*, *stringr*, *plyr* and *KEGGgraph*. These should be installed automatically when you install *NFP* with biocLite() as follows:

```{R install, eval=FALSE}
## install release version of mmnet
source("http://bioconductor.org/biocLite.R")
biocLite("NFP")

##install the latest development version
useDevel()
biocLite("NFP")
```

Or users can install the latest development version from github. To install packages from GitHub, you first need install the devtools package on your system with
`install.packages("devtools")`. Note that devtools sometimes needs some extra
non-R software on your system -- more specifically, an Rtools download for
Windows or Xcode for OS X.

```{r install-pkg-github, eval=FALSE}
## install NFP from github
if (!require(devtools))
  install.packages("devtools")
devtools::install_github("yiluheihei/NFP")
```

### Getting started

After installation, the *NFP* is ready to load into the current workspace
by the following codes to the current workspace by typing or pasting the
following codes:

```{r load-pkg,eval=TRUE, include=FALSE}
library(NFP)
```
```{r load-pkg2,eval=FALSE}
library(NFP)
```

To see a brief overview of the package:

```{r eval=FALSE}
library(help = 'NFP')
```

To get help on any function in this package

```{r eval=FALSE}
help(package='NFP')
```

To see the vignettes of this package:

```{r eval =FALSE}
vignette('NFP')
```
  
## 


本章我们将通过对kegg pathway中的疾病网络进行网络指纹分析，来帮助用户学习如何使用NFP包

### Generate well-studied basic reference networks, 

network fingerprint的基本思想是把biomedical networks映射到well-stuied basic Networks. 
KEGG PATHWAY is a collection of manually drawn pathway maps representing our knowledge on the molecular interaction and reaction networks. Since its first introduction in 1995, KEGG PATHWAY has been widely used as a reference knowledge base for understanding biological pathways and functions of cellular processes. The knowledge from KEGG has proven of great value by numerous work in a wide range of fields [Kanehisa et al., 2008].
networks. ... (为什么选择KEGG pathway作为默认的参考网络)，... 所以默认情况下我们选择使用
KEGG pathway作为参考网络.

NFP provide function *load_KEGG_refnet* to retrieve the kegg pathway maps with kegg
API. KEGG pathway中只有map一类的pathway是手动绘制的，然后对于不同organism的pathway
是参考map来自动生成organism-specific pathway. The *organism* parameter indicate the organism name of kegg pathway maps.

```{R eval=FALSE}
kegg_refnet <- load_KEGG_refnet(organism = 'hsa')
```
To generate the kegg pathway map as the NFP 
We defined a new S4 class **NFPrefnet** to store the NFP reference networks.
并且提供了物种方法，net,group,subnet,show和name来对这个类进行操作，关于这五个方法
的详细使用说明参考包的函数帮助。

显然用户还可以自定义一个NFPRefnet类来作为指纹印记计算的参考网络,对于这个类的详细
构成可以参考*NFPRefnet-class*的文档：

```{r eval=FALSE}
new("NFPRefnet",network = ref_net, name = names, group = group, 
  organism = ref_net_organism)
selected_group <- group(kegg_refnet)$name[c(1,2)]
NFPnet <- subnet(kegg_refnet,selected_group)
show(NFPnet)
```

Function *save_kegg_refnet* is provided to save the loaded reference networks. Users can reload it simply with *load*.

```{r eval=FALSE}
save_kegg_refnet(kegg_refnet, file = 'kegg_refnet')
load('kegg_refnet')
```

### 计算NFP

NFP的算法包括了三个步骤，1.网络merging 2.聚类, 3 similarity scoring（崔的文章中应该
有详细说明，分别对这三个步骤进行简要介绍。

N函数cal_sim_score用来计算网络指纹，nperm是指前面所述similarity score中随机生成
网络的次数。NFP中定义了NFP类来存储网络指纹的计算结果,同时也提供了plot， sub_NFP，show等5个方法来对NFP类操作

我们选择kegg中的疾病网络作为query network来分别计算他们的网络指纹并进行比较（参考崔文章）

```{r eval=FALSE}
query_net <- data(kegg_disease_pathway)
NFP_score <- lapply(query_net, calc_sim_score,NFPnet = NFPnet, nperm = 100)
show(NFP_score)
randomized_score  <- nperm_score(NFP_score)
sd(randomized_score)
mean(randomized_score)
cluster_info(randomized_score)
```

NFP_score存储了网络指纹全面的信息，包括了标准化前的相似度，标准化后的相似度，
参考网络的名称和分类，和网络比较中的cluster信息

### 可视化

NFP中提供了plot_NFP来对网络指纹结果可视化，可以比较不同query network的fingerprint.
plot_NFP的详细用法参考该函数的帮助文档
 ```{r eval=FALSE}
 plot(NFP_score)
 ```

结果分析。。。。这一部分我来写

## Future

1. 覆盖更多的参考通路，如reactome， HumanCyc，NCI Pathway interaction， panther
使分析更全面

2. 输入支持基因表达列表

## Acknowledgements

感谢李非 感谢小贺 感谢bioconductor的工作人员 ~.~

## Conclusion

高通量实验技术的发展，使得关于生物网络数据飞速增长，NFP可以用来分析...(NFP的应用
潜力，参考崔的文章的conclustion

## Session Information

The version number of R and packages loaded for generating the vignette were:

```{R echo=FALSE}
sessionInfo()
```
## Cleanup


This is a cleanup step for the vignette on Windows; typically not
needed for users.

```{r clean-up}
allCon <- showConnections()
socketCon <- as.integer(rownames(allCon)[allCon[, "class"] == "sockconn"])
sapply(socketCon, function(ii) close.connection(getConnection(ii)) )
```
